Social Conditions of Fear

### 2023-11-21 scripts/manuscript.qmd
select the variables we need

**Sociodemographics Variables**
1. "born": Were you born in this country?
2. "age"
3. "sexnow1": Do you describe yourself as male, female, or transgender? 
4. "sexornt": Which of the following best describes you? 
5. "racerank1": If you had to choose, which of these races do you identify most with?
6. "hispanic": Are you Spanish, Hispanic, or Latino/Latina? IF YES: Which group are you from?
7. "degree": Respondent's degree.
8. "uscitzn": Are you a US citizen?
9. "dwelown": (Do you/Does your family) own your (home/apartment), pay rent, or what?

**Other Controls**
1 "attend": How often do you attend religious services?
2. "raclive": Are there any ("whites" for black respondents, "blacks" for non-black respondents) living in this neighborhood now?
3. "happy": Taken all together, how would you say things are these days--would you say that you are very happy, pretty happy, or not too happy?
4. "health": Would you say your own health, in general, is excellent, good, fair, or poor?
5. "helpful": Would you say that most of the time people try to be helpful, or that they are mostly just looking out for themselves?
6. "fair": Do you think most people would try to take advantage of you if they got a chance, or would they try to be fair?
7. "trust": Generally speaking, would you say that most people can be trusted or that you can't be too careful in dealing with people?

@@

```{r}
#| label: gss 2022
gss2022 <- gss %>% 
  filter(year == "2022")

@@

>>>>

**Sociodemographics Variables**
1. "born": Were you born in this country?
2. "age"
3. "sexnow1": Do you describe yourself as male, female, or transgender? 
*This is self-described gender.*
4. "sex": Code respondent's sex
*This is gender presentation as interpreted by the interviewer.*
4. "sexornt": Which of the following best describes you? 
5. "racerank1": If you had to choose, which of these races do you identify most with? 
*Kept this race variable here instead of "race" because it allows more heterogeneity within group.*
6. "hispanic": Are you Spanish, Hispanic, or Latino/Latina? IF YES: Which group are you from?
7. "degree": Respondent's degree.
8. "uscitzn": Are you a US citizen?
9. "dwelown": (Do you/Does your family) own your (home/apartment), pay rent, or what?

**Other Controls**
1 "attend": How often do you attend religious services?
2. "raclive": Are there any ("whites" for black respondents, "blacks" for non-black respondents) living in this neighborhood now?
3. "happy": Taken all together, how would you say things are these days--would you say that you are very happy, pretty happy, or not too happy?
4. "health": Would you say your own health, in general, is excellent, good, fair, or poor?
5. "helpful": Would you say that most of the time people try to be helpful, or that they are mostly just looking out for themselves?
6. "fair": Do you think most people would try to take advantage of you if they got a chance, or would they try to be fair?
7. "trust": Generally speaking, would you say that most people can be trusted or that you can't be too careful in dealing with people?
8. "partnrs5": since February/March 2015, and including the past 12 months, how many sex partners have you had in that five year period?

# set up

@@

```{r}
#| label: gss 2022
gss2022 <- gss %>% 
  filter(year == "2022") %>% 
  select("year", "id", "age", "sex", "sexnow1", "sex", "degree", "race", "born", "attend", "raclive", "happy", "health", "helpful", "fair", "trust", "fear",  "partnrs5", "sexornt", "hispanic", "racerank1", "uscitzn", "dwelown")

@@

# recode variables
